Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
for real this time

Indiscernibility is a robust measure: it is almost perfectly
correlated for various CCLM (transformer, lstm and various $c$) $M$.
\jp{other r's}
\begin{figure}
  \pplscatter{lstm-3-1_lmcc}{transformer-3-3_lmcc}
  \caption{%
    Correlation between indeterminacy for the best LSTM ($c = 1$) and transformer ($c = 3$) models
    (Pearson's r = \num{0.99} p < \num{0.0001}).
  }
  \label{fig:lmcc_ppl}
\end{figure}

>>>>

Indiscernibility is a robust measure: it is almost perfectly
correlated for various CCLM (transformer, lstm and various $c$) $M$.
\jp{other r's}
\begin{figure}
  \pplscatter{lstm-3-1_lmcc}{transformer-3-3_lmcc}
  \caption{%
    Correlation between indiscernibility for the best LSTM ($c = 1$) and transformer ($c = 3$) models
    (Pearson's r = \num{0.99} p < \num{0.0001}).
  }
  \label{fig:lmcc_ppl}
\end{figure}
